---
title: "Aho_livesession5assignment"
author: "Andy Ho"
date: "June 11, 2018"
output: html_document
---

#### 1. Data Munging from yob2016.txt file
  + A. Importing the file into R and assigning to object 'df'
```{r}
df <- read.table("yob2016.txt", sep = ';', header = FALSE)
head(df)
```
  + B. Display the summary and structure of df
```{r}
str(df)
summary(df)
```
  + C. Name with three y's in list
```{r}
names(df) <- c("First_Name", "Gender", "Frequency")
head(df)
grep("yyy$", df$First_Name, value = TRUE)
```
  + D. Remove 'Fionayyy' from the list
```{r}
remove <- c("Fionayyy")
df2 <- df[! df$First_Name %in% remove,]
grep("yyy$", df2$First_Name, value = TRUE)
y2016 <- df2
head(y2016)
```

####2. Data Merging
  + A. Import yob2015.txt and store into object df
```{r}
df <- read.table("yob2015.txt", sep = ',', header = FALSE)
y2015 <- df
str(y2015)
```

  + B. Display the last ten rows of data frame.  All the names start with the letter Z, associated to male gender, and each have a frequency of 5.
```{r}
names(y2015) <- c("First_Name", "Gender", "Frequency")
tail(y2015, 10)
```

  + C. Merging y2016 and y2015 by Name column.
```{r}
final <- merge(y2015, y2016, by=c("First_Name", "Gender"), all=TRUE)
names(final) <- c("First_Name","Gender", "Freq_2015", "Freq_2016")
any(is.na(final))
colSums(is.na(final))
final[is.na(final)]=0
colSums(is.na(final))
str(final)
```

####3. Utilizing 'final' object for the following
  + A. Create new column called "Total" in final.  How many people were given popular names?
```{r}
final$Total <- 0
head(final)
final$Total <- final$Freq_2015 + final$Freq_2016
cat ("Total number of people using popular names is", sum(final$Total), ".")
```
  + B. Sort the data by Total.  What are the top 10 most popular names?
```{r}
finalbytotal <- final[order(-final$Total),]
head(finalbytotal, 10)
```
  + C. Top 10 Girl Names
```{r}
final_girl <- subset(finalbytotal, finalbytotal$Gender == "F")
final_girl <- final_girl[order(-final_girl$Total),]
head(final_girl, 10)
```

  + D. Top 10 girl names and totals in CSV file: "Top_10_Girl_Names.csv"
```{r}
final_girl_10 <- head(final_girl, 10)
final_girl_10 <- final_girl_10[,c("First_Name","Gender","Total")]
final_girl_10
write.csv(final_girl_10, file = "Top_10_Girl_Names.csv", row.names = FALSE)
```

####4. Upload to Github
  + URL: https://github.com/atho316/MSDS6306-Homework-Unit_5